Asteroseismology AI-Driven Seismic Event Detection for Extra-Terrestrial Missions\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2025-05-07 paper.tex
helo added
abstract added

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Conference Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%hello khabab
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Asteroseismology  AI-Driven Seismic Event Detection for Extra-Terrestrial Missions\\
% {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
% should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{abstract}
    Planetary seismology faces significant challenges in transmitting continuous seismic data
    due to bandwidth and power constraints. Traditional event detection methods generate 
    numerous false positives, leading to inefficient data transmission. This paper presents 
    Asteroseismology, an AI-enhanced seismic event detection framework that integrates 
    classical phase-picking algorithms with machine learning to optimize seismic data 
    processing for space missions. The workflow begins with automatic bandpass filtering, 
    outlier removal, and normalization to enhance signal clarity. A Short-Term Average to 
    Long-Term Average (STA/LTA) analysis is then applied to detect candidate events, followed 
    by a filtering mechanism that refines initial picks based on characteristic function 
    slopes. The final step employs a Convolutional Neural Network (CNN), trained on seismic 
    data from the Apollo Lunar Surface Experiments Package (ALSEP) and NASA’s Mars InSight
    mission, to distinguish true seismic events from noise, ensuring high precision while 
    minimizing false detections. Designed for computational efficiency, the system
    processes a month’s worth of seismic data in under 60 seconds on an average processor.
    It also features six tunable parameters, allowing adaptation to different planetary
    environments and mission constraints. Initial results demonstrate that the CNN, despite
    limited training, achieves over 80 percent event detection accuracy with a false
    positive rate of approximately 5 percent. Future enhancements include refining the
    CNN within an Auxiliary Classifier Conditional GAN (AC-GAN) framework to further 
    improve detection reliability. This AI-driven approach enables autonomous seismic 
    data analysis onboard spacecraft, significantly reducing the need for raw data 
    transmission and paving the way for more efficient planetary and lunar seismology 
    missions.
\end{abstract}

\begin{IEEEkeywords}
    Seismic Event Detection, Planetary Seismology, Machine Learning, 
    CNN, STA/LTA, AI in Space Exploration.
\end{IEEEkeywords}
